Internal models of type theory and internal higher categories for the Univalent Foundations

### 2014-03-02 article-models-tt.tex
renamed section 3

\section{Type theory before type constructors}\label{tt}
In this section we give a description of type theory before basic
constructors and with explicit extension, weakening and substitution. We will
formulate the type theory in such a way that contexts aren't lists of variable
declarations. The main reason is that we don't see variable declarations in the
models either. This way we also set out to a more algebraic approach of type
theory and higher category theory. Thirdly, we will not have to be burdened with
comments about variables being bounded or not, or fresh or not occuring at all.

@@

>>>>

\section{Structural type theory}\label{tt}
In this section we give a description of type theory before basic
constructors and with explicit extension, weakening and substitution. We will
formulate the type theory in such a way that contexts aren't lists of variable
declarations. The main reason is that we don't see variable declarations in the
models either. This way we also set out to a more algebraic approach of type
theory and higher category theory. Thirdly, we will not have to be burdened with
comments about variables being bounded or not, or fresh or not occuring at all.

@@

Pretty type theory should be such that if you write down two contexts, families
or terms in exactly the same way, then they are the same, and there should be
notational shortcuts for extension, weakening and substitution which make
this interesting.
